Concurrent Priority Queues

### 2014-03-24 presentation/presentation.tex
Add new sections
Related work
PQ introduction

\documentclass{beamer}

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage{default}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

@@

@@

\begin{frame}{Hello World}
Hello
\end{frame}

\begin{frame}[allowframebreaks]{Bibliography}
\nocite{*}
\printbibliography
\end{frame}

>>>>

\documentclass[usenames,dvipsnames]{beamer}

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage{default}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{lmodern}

@@

\lstset{
    language=C++,
    basicstyle=\ttfamily,
    keywordstyle=\color{OliveGreen},
    commentstyle=\color{Gray},
    captionpos=b,
    breaklines=true,
    breakatwhitespace=false,
    showspaces=false,
    showtabs=false,
    numbers=none,
}

@@

\begin{frame}{Outline}
\begin{minipage}[t][10em][t]{\linewidth}
\tableofcontents
\end{minipage}
\end{frame}

% --------------------------------------------------------------------------------------------------
\section{Introduction}
% --------------------------------------------------------------------------------------------------

\begin{frame}[fragile]{Introduction}
Priority Queues (PQs):

\begin{itemize}
\item Standard abstract data structure
\item Used widely in algorithmics, operating systems, task scheduling, etc
\item Interface consists of two $O(\log n)$ operations:

\begin{lstlisting}
void Insert(pq_t *pq, key_t k, value_t v)
bool DeleteMin(pq_t *pq, value_t *v)
\end{lstlisting}

\item Typical backing data structures: heaps \& search trees
\end{itemize}

\end{frame}

% --------------------------------------------------------------------------------------------------
\section{Related Work}
% --------------------------------------------------------------------------------------------------

\begin{frame}{Related Work}
\begin{itemize}
\item Non-standard synchronization primitives
    \begin{itemize}
    \item \citeauthor{liu2012lock}: Array-based PQ with \lstinline|ExtractMany|
    \item \citeauthor{israeli1993efficient}: Wait-free PQ
    \end{itemize}

\item Bounded range priorities
    \begin{itemize}
    \item \citeauthor{shavit1999scalable}: Combining funnels \& bins
    \end{itemize}

\item PQs in distributed memory systems
    \begin{itemize}
    \item \citeauthor{sanders1998randomized}: Local PQs, \lstinline|Insert| at random processor
    \end{itemize}

\item Relaxed data structures
    \begin{itemize}
    \item \citeauthor{kirsch2012fast}: k-FIFO queues
    \end{itemize}

\end{itemize}
\end{frame}

% --------------------------------------------------------------------------------------------------
\section{Concepts and Definitions}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Fine-grained Locking Heaps}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Lock-free Priority Queues}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Relaxed Priority Queues}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Conclusion}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{References}
% --------------------------------------------------------------------------------------------------

\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}
